\subsection{Discipline}
		During game time (i.e. while the OnlyRugby app is being used to log the information of a match currently being played ) 
		the Discipline function will be used each time a player performs an infraction that causes them to reveive a card.
		The Discipline function works as follows:
		\begin{enumerate}
			\item Once the user has pressed the button to log the disciplinary action's information they are redirected to a page which asks them to indicate which team's player was given a card, by pressing either of two buttons which each
			have the names of the respective teams on them.
			\item The app then redirects the user to another page which has 15 buttons representing the 15 on-field players of the previously selected team. Each button has the player's position/jersey number on it 
			as well as the player's name (if that information is provided on the database). This page also has an 'Unknown' button incase the user, for some reason, is not sure who the player being disciplined is. The user is asked to select one of these players/buttons as the player who was disciplined.
			\item The app then redirects the user to another page which has 3 buttons, to indicate if a white, yellow or red card was given.
			
		\end{enumerate}
	On all of the above described pages there are also buttons labeled 'Cancel' (to cancel logging the discipline) and 'Back' which redirects the user to the previous page and ignores the information that was logged on the page it is now leaving.